% Bibliography
%*****************************************************************************************************

% Bewtween \begin{thebibliography}{99} and \end{thebibliography} kann das Literaturverzeichnis erweitert werden. 
% The text in the braces directly after \bibitem can be used for citation with the \cite command.


\begin{thebibliography}{99}
\addcontentsline{toc}{chapter}{Bibliography}

\bibitem{Pruett2008} \textsc {C. Pruett,}  ``Temporal large-eddy simulation: theory and implementation,'' Theor. Comput. Fluid Dyn. \textbf{22}, 275 (2008).

\bibitem{Smagorinsky1963} \textsc {J. Smagorinsky,} ``General circulation experiments with the primitive equations. I. The basic experiment,'' Mon. Weather Rev. \textbf{91}, 99 (1963).

\bibitem{Stolz1999} \textsc {S. Stolz, and N.A. Adams,}  ``An approximate deconvolution procedure for large-eddy simulation,'' Phys. Fluids  \textbf{11}, 1699 (1999).

\bibitem{Germano1991} \textsc {M. Germano, U. Piomelli, P. Moin and W.H. Cabot,} ``A dynamic subgrid-scale eddy viscosity model,'' Phys. Fluids \textbf{3}, 1760 (1991).

\bibitem{Pruett2000} \textsc {C. Pruett,}  ``Eulerian Time-Domain Filtering for Spatial Large-Eddy Simulation,'' AIAA J. \textbf{38}, 1634 (2000).

\bibitem{Jenny2016} \textsc {P. Jenny,}  ``Unsteady RANS closure,'' Unpublished (2016).

\bibitem{Stolz2001} \textsc {S. Stolz, N.A. Adams, and L. Kleiser,}  ``An approximate deconvolution model for large-eddy simulation with application to incompressible wall-bounded flows,'' Phys. Fluids  \textbf{13}, 997 (2001).

\bibitem{Akervik2006} \textsc {A. \AA kervik, L Brandt, D. S. Henningson, J. H\oe pffner, O. Marxen, and P. Schlatter,}  ``Steady solutions of the Navier-Stokes equations by selective frequency damping,'' Phys. Fluids  \textbf{18}, 068102 (2006).

\bibitem{Toth2000} \textsc {G. T\'oth,}  ``The $\nabla \cdot B=0$ Constraint in Shock-Capturing Magnetohydrodynamics Codes,'' J. Comput. Fluids \textbf{161}, 605 (2000).

% Citation format for a book
%\bibitem{citation_reference} \textsc {Author,}  \emph{Book Title}, year, Publisher.
 
\end{thebibliography}
